---
title: "Sight Latency Test Analysis Followup"
author: "lane"
date: "24-Jul-2017"
output:
  html_document:
    toc: true
    toc_depth: 2
  html_notebook: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library(ggplot2)
#library(plyr)
#library(dplyr)
library(tidyverse)
```

Note: this borrows from Cole's original analysis.

## Initialization of data frames

Currently, the folder variable is set to be the path to the csvHolder file in my downloads section. It needs to be set to yours when you use this.

```{r init}
# folder variable should be changed to be the path to the csvHolder file
folder <- "csvHolder/"

latencyFiles <- list.files(path=paste(folder, "latency", sep='/'), pattern="*.csv")
#latency <- lapply(latencyFiles, function(file){ read.csv( paste(folder, "latency", file, sep='/'), header = FALSE)} )
latencyFiles <- sapply(latencyFiles, function(file) { paste(folder, "latency", file, sep='/') } )
latency <- tibble()
latency <- do.call(rbind,lapply(latencyFiles, function(f) { read.csv(f, header=FALSE) }))

# Events Setup
eventsFiles <- list.files(path=paste(folder, "events", sep='/'), pattern="*.csv")
events <- tibble()
eventsFiles <- sapply(eventsFiles, function(file) { paste(folder, "events", file, sep='/') } )
events <- do.call(rbind,lapply(eventsFiles, function(f) { read.csv(f, header=FALSE) }))

# add events columns
colnames(events) <- c('event_type', 'date', 'time_stamp', 'x_position', 'y_position', 'target_element', 'target_ID', 'key_pressed', 'collection_type')
colnames(latency) <- c('event_type', 'latency_ms', 'instrumentation')

# convert row names to columns
events <- rownames_to_column(events, "sourcefile")
latency <- rownames_to_column(latency, "sourcefile")

# add dataset based on filename
events <- events %>%
 tidyr::extract(
    sourcefile, c("dataset"), "(255|exo)", 
    remove = FALSE
  ) 
latency <- latency %>%
 tidyr::extract(
    sourcefile, c("dataset"), "(255|exo)", 
    remove = FALSE
  ) 

# add user based on filename
events <- events %>%
   tidyr::extract(
    sourcefile, c("user"), "(255-0|255-1|255-2|255-3|exo-0|exo-1|exo-2|exo-3)", 
    remove = FALSE
  )
latency <- latency %>%
   tidyr::extract(
    sourcefile, c("user"), "(255-0|255-1|255-2|255-3|exo-0|exo-1|exo-2|exo-3)", 
    remove = FALSE
  )

```

## Distribution of User Interactions

```{r distribplot, fig.width=6, fig.asp=0.618}

events %>% 
  group_by(dataset, user) %>% 
  summarise(count=n()) %>% 
  arrange(dataset, count) %>% 
  ggplot( aes(x=dataset, y=count, group=reorder(user, -count)) ) +
    geom_col(position=position_dodge(width=0.8), width=0.7) +
    labs(
      x="Visualization Condition (1 bar / participant)", 
      y="Interaction Count", 
      title="Distribution of Interactions, Per Participant"
      ) +
    theme_bw()
    
```

## Cumulative Distribution Charts
```{r cdfplot, fig.width=6, fig.asp=0.618}

latency %>% 
  ggplot() +
    stat_ecdf(aes(x=latency_ms, colour=instrumentation)) +
    scale_y_continuous(labels=scales::percent) + 
    coord_cartesian(xlim=c(0, 50)) +
    labs(
      x="Latency (ms)", 
      y="Percent of Interactions", 
      color="Tracking", 
      title="Cumulative Distribution of Interaction Latency"
    ) +
    theme_bw()

```

## Stacked Plots

First, we do the originals

```{r stackedplot, fig.width=6, fig.asp=0.618}

latency %>% 
  filter(latency_ms < 500) %>% 
  ggplot(aes(x=latency_ms, fill=event_type)) +
    geom_histogram(binwidth=50, position="fill") +
    facet_grid(. ~ instrumentation) +
    theme_bw()

latency %>% 
  filter(latency_ms >= 500) %>% 
  ggplot(aes(x=latency_ms, fill=event_type)) +
    geom_histogram(binwidth=500, position="fill") +
    facet_grid(. ~ instrumentation) + 
    theme_bw()
```
Next, we roll interactions up by type to address the overcrowded color problem
```{r}

latency$event_category <- latency$event_type
latency$event_category <- stringr::str_replace(latency$event_category,"transition.*","animation")
latency$event_category <- stringr::str_replace(latency$event_category,"key.*","key")
latency$event_category <- stringr::str_replace(latency$event_category,"drag.*","drag")
latency$event_category <- stringr::str_replace(latency$event_category,"mouse.*","mouse")
latency$event_category <- stringr::str_replace(latency$event_category,".*click.*","mouse")
latency$event_category <- stringr::str_replace(latency$event_category,"scroll","mouse")
latency$event_category <- stringr::str_replace(latency$event_category,"blur|devicelight|focus|load|pageshow|resize","device")


latency %>% 
  filter(latency_ms < 500) %>% 
  ggplot(aes(x=latency_ms, fill=event_category)) +
    geom_histogram(binwidth=100, position="fill") +
    facet_grid(. ~ instrumentation)

# facet on type
latency %>% 
  filter(latency_ms > 100) %>% 
  ggplot(aes(x=latency_ms)) +
    geom_histogram(binwidth=50) +
    facet_grid(event_category ~ instrumentation, scales = "free")

latency %>% 
  filter(latency_ms >= 500) %>% 
  ggplot(aes(x=latency_ms, fill=event_category)) +
    geom_histogram(binwidth=500, position="fill") +
    facet_grid(. ~ instrumentation)

```

